Consistency scores in text data

### 2020-08-11 outputs/documents/paper.Rmd
Minor updates to the paper.

We will use the `textcnt()` function to turn the training corpus into tri-grams. The most important argument of this function is the _corpus_, as well as the _n_ to set the number of words in a sequence, _method_ to determine which type of counts to compute, and _split_ to designate the regular expression pattern for splitting. The function outputs a `textcnt` object, which is essentially a table with each tri-gram and their counts (@citetau).

@@

We then manually added an end of sentence token </s> to the end of each sentence.

@@

There are a few packages for implementing a Word2Vec model in R. The packages are `rword2vec` by @rword2vec and `word2vec` by @word2vecR. Both packages use the same algorithm that Word2Vec uses to produce word representations, but they do not have an affiliation with Google. Another way to implement a Word2Vec model in R is through Keras package. Keras is an API for deep learning written in Python [@chollet2015keras] and the Keras package provides an R interface to Keras [@kerasR2020]. RStudio published a tutorial for implementing the skip-gram model of Word2Vec [@falbel2017word] through Keras. We intend to follow this tutorial as the approach to implement a Word2Vec model. There are three basic steps within the Keras deep learning framework: first is to prepare the data, second is to define the model and third is to train and evaluate the model. Following the steps, we first downloaded a the [Amazon Fine Foods Reviews dataset from Stanford] [@amzfinefooddata] and preprocess the text into tokens. Then we defined a model that mimics the skip-gram algorithm of Word2Vec in a function called `skipgrams_generator()`. The embedding dimensions, the size of the context window and the number of samples are configurable within this function. Finally, we used the `fit_generator()` function of Keras to train the model. **What's supposed to happen:** As a result, a embedding matrix is obtained and serves as the look-up table of the word vectors. **What really happened:** However, the training process was stuck in the operation of `fit_generator()` function. According to Stack Flow this might be an issue of incompatible versions between Keras and Tensorflow. More investigation is needed.

@@

There are more than one way to implement GloVe word embedding model in R. One way is to load GloVe embeddings into a frozen Keras Embedding layer [@kerasglove] using the `Keras` R package [@kerasR2020]. Another way, as mentioned and briefly demonstrated by Rstudio in their blog post, is to use the `text2vec` package developed by @text2vec. Keras published a blog post on pre-trained word embeddings through GloVe in R. In this project, we intend to follow the blog post for implementing GloVe through the Keras R package [@kerasglove]. The blog post is aimed to create a word embedding model for text classification. However, we will only use the guide create a embedding index and skip the steps of text classification. Instead of building a model for word embedding from scratch as we did for the skip-gram model of Word2Vec, here we are merely loading the Glove model and its pre-trained word vectors as an index. The word embedding index is then saved to an R environment.

>>>>

We will use the `textcnt()` function to turn the training corpus into tri-grams. The most important argument of this function is _corpus_, as well as _n_ to set the number of words in a sequence, _method_ to determine which type of counts to compute, and _split_ to designate the regular expression pattern for splitting. The function outputs a `textcnt` object, which is essentially a table with each tri-gram and their counts (@citetau).

@@

We then manually added an end of sentence token, `</s>`, to the end of each sentence.

@@

There are a few packages for implementing a word2vec model in R, including `rword2vec` [@citerwordvecchaware] and `word2vec` [@citewordvecwijffels]. Both packages use the same algorithm. Another way to implement a word2vec model in R is through Keras which is an API for deep learning written in Python [@chollet2015keras] for which the `keras` package provides an R interface [@citekeras].

Here, we follow @falbel2017word to implement a skip-gram model of word2vec through Keras. There are three steps in the Keras deep learning framework: 1) prepare the data; 2) define the model; and 3) train and evaluate the model. **(Ke-Li: Can we change this to be a different dataset please?)** Following these steps, we first downloaded the **(Ke-Li: Is there a reason this is in brackets?)** [Amazon Fine Foods Reviews dataset from Stanford] [@amzfinefooddata] and preprocess the text into tokens.

**(Ke-Li: Add code.)**

We then define a model that mimics the skip-gram algorithm of word2vec using the function `skipgrams_generator()`.

**(Ke-Li: Add code.)**

The embedding dimensions, the size of the context window and the number of samples are configurable within this function.

Finally, we use the `fit_generator()` function to train the model.

**(Ke-Li: Add code.)**

**What's supposed to happen:** As a result, a embedding matrix is obtained and serves as the look-up table of the word vectors. **What really happened:** However, the training process was stuck in the operation of `fit_generator()` function. According to Stack Flow this might be an issue of incompatible versions between Keras and Tensorflow. More investigation is needed.

@@

There are a variety of ways to implement GloVe word embedding models in R. One is to load GloVe embeddings into a frozen Keras Embedding layer [@kerasglove] using the `Keras` R package [@kerasR2020]. This means **(Ke-Li: Add what it means please.)** Another way, is to use the `text2vec` package [@text2vec].

Here we follow **CITE** to implement GloVe using the `keras` R package [@kerasglove]. The blog post is aimed to create a word embedding model for text classification. However, we will only use the guide create a embedding index and skip the steps of text classification. Instead of building a model for word embedding from scratch as we did for the skip-gram model of Word2Vec, here we are merely loading the Glove model and its pre-trained word vectors as an index. The word embedding index is then saved to an R environment.

**[As before, we need code and examples here]**
